Title

### 2023-08-17 manu-draft.qmd
seagrass change fig added

@@

-   Temp: 20-30 (range, @lewis1985, @zieman75), 30-31 (upper, from SS)

@@

@@

![Conceptual stressor diagram](figs/concept.png){#fig-concept} {{< pagebreak >}}

>>>>

Seagrass changes over time in @fig-seagrasschg.

@@

-   Temp: 20-30 (range, @lewis1985, @zieman1975), 30-31 (upper, from SS)

@@

Other areas showing seagrass loss - Florida Bay is different, less water flowing out of everglad and compounding SLR has elevated salinity and likely stress in other direction. Also, Biscayne Bay and IRL is a lot like OTB, poor flushing for example.

@@

![Seagrass changes over time in Tampa Bay for (a) areal coverage and (b) frequency occurrence of major species.  Changes are shown for major bay segments. Note the different time scale between (a) and  (b).  Coverage maps in (a) began in 1988 and seagrass transect monitoring in (b) began in 1998. Red lines in (a) show approximate capacity of seagrass coverage based on the baywide target of 40,000 acres. OTB: Old Tampa Bay, HB: Hillsborough Bay, MTB: Middle Tampa Bay, LTB: Lower Tampa Bay. ](figs/seagrasschg.png){#fig-seagrasschg}

{{< pagebreak >}}

![Conceptual stressor diagram](figs/concept.png){#fig-concept}

{{< pagebreak >}}
